# Commercial Fishery Revenue

**Description** Commercial fishery revenue is a direct indicator of ecosystem services provided to coastal economies of the CCE. Commercial revenue data are best summarized by the Pacific Fisheries Information Network (PacFIN; pacfin.psmfc.org). Revenues are calculated based on consumer price indices in current year (e.g., 2024) dollars. Status and trends are estimated relative to a frame of reference of 1991-2020. In most cases, revenue data for the most recent reporting year are only complete through the latter months (e.g., October-December); these data are updated in the next annual cycle.

Commercial revenue data are reported coastwide and by state (CA, OR, WA) by fishery species category.

**Indicators**

```{r}
#| echo: false
#| message: false
#| eval: true
source("_getmeta.R")

erddap_id='cciea_AC_revenue'
meta=getMetadata(erddap_id)
num_ind = nrow(meta)
```


```{r}
#| echo: false
#| results: 'asis'
cat("* <b>Species:</b>\n")
for (i in 1:num_ind){
cat("     + ",meta$ERDDAP_query_value[i],"\n")
}
```

```{r}
#| echo: false
#| results: 'asis'
cat("* <b>Component Category: </b>", meta$Component_Section[1],"\n")
cat("* <b>Data Steward: </b>",meta$Contact[1],"\n")
cat("* <b>Institution: </b>",meta$Institution[1],"\n")
cat("* <b>Source Data: </b>",meta$Source_Data[1],"\n")
if(meta$Additional_Calculations[1]!="")cat("* <b>Additional Calculations: </b>",meta$Additional_Calculations[1],"\n")
```

**Data extraction**

```{r}
#| echo: false
#| results: 'asis'
cat("ERDDAP&trade; link: <https://oceanview.pfeg.noaa.gov/erddap/tabledap/",erddap_id,".html>",sep="")
```

**Data analysis**

**References**
