# Fishery Landings and Revenues

**Description** Commercial landings and revenue data are best summarized by the Pacific Fisheries Information Network (PacFIN; pacfin.psmfc.org), and recreational landings are best summarized by the Recreational Fisheries Information Network (RecFIN; www.recfin.org). Landings provide the best long-term indicator of fisheries removals. Revenues are calculated based on consumer price indices in 2023 dollars. Status and trends are estimated relative to a frame of reference of 1991-2020.

```{r}
#| echo: false
#| message: false
#| eval: true
source("_getmeta.R")

erddap_id='cciea_AC_landings'
meta=getMetadata(erddap_id)
num_ind = nrow(meta)
```


```{r}
#| echo: false
#| results: 'asis'
cat("* <b>Species:</b>\n")
for (i in 1:num_ind){
cat("     + ",meta$ERDDAP_query_value[i],"\n")
}
```

```{r}
#| echo: false
#| results: 'asis'
cat("* <b>Component Category: </b>", meta$Component_Section[1],"\n")
cat("* <b>Data Steward: </b>",meta$Contact[1],"\n")
cat("* <b>Institution: </b>",meta$Institution[1],"\n")
cat("* <b>Source Data: </b>",meta$Source_Data[1],"\n")
if(meta$Additional_Calculations[1]!="")cat("* <b>Additional Calculations: </b>",meta$Additional_Calculations[1],"\n")
```

**Data extraction**

**Data analysis**
