# Habitat Compression Index

```{r get-file-from-google-drive}
#| echo: false
#| message: false
#| eval: true
erddap_id='cciea_OC_HCI'
source("_getmeta.R")
meta=getMetadata(erddap_id)
num_ind = nrow(meta)
```

**Indicators**

```{r}
#| echo: false
#| results: 'asis'

for (i in 1:num_ind){
cat("* <b>",meta$Title[i],"</b>\n")
cat("     + *Component Category: *", meta$Component_Section[i],"\n")
cat("     + *Data Steward: *",meta$Contact[i],"\n")
cat("     + *Institution: *",meta$Institution[i],"\n")
cat("     + *Additional Calculations: *",meta$Additional_Calculations[i],"\n")
cat("     + *Source Data: *",meta$Source_Data[i],"\n")

}
```

**Description** The Habitat Compression Index (HCI) is the area of cool habitat along the coast, which is suitable for a diverse and productive portion of the CCE food web. HCI is estimated in four biogeographic provinces along the shelf within the CCE.

**References** @Santora2020, @Schroeder2022

**Public availability statement** Source data are publicly available.

**Data sources** Surface temperature data are the 2 m temperature levels of the University of California Santa Cruz 31-year historical reanalysis (<https://oceanmodeling.ucsc.edu/reanalccs31/>) and near-real-time (NRT; <https://oceanmodeling.ucsc.edu/ccsnrt/>) data-assimilative models.

**Data extraction**

**Data analysis**
