
# Habitat Compression Index


**Description** The Habitat Compression Index (HCI) is the area of cool habitat along the coast, which is suitable for a diverse and productive portion of the CCE food web. HCI is estimated in four biogeographic provinces along the shelf within the CCE.

```{r}
#| echo: false
#| message: false
#| eval: true
source("_getmeta.R")

erddap_id='cciea_OC_HCI'
meta=getMetadata(erddap_id)
num_ind = nrow(meta)
```


```{r}
#| echo: false
#| results: 'asis'
cat("* <b>Latitude bands:</b>\n")
for (i in 1:num_ind){
cat("     + ",meta$latitude[i],"-",meta$latitude2[i],"N</i>\n")
}
```

```{r}
#| echo: false
#| results: 'asis'
cat("* <b>Component Category: </b>", meta$Component_Section[1],"\n")
cat("* <b>Data Steward: </b>",meta$Contact[1],"\n")
cat("* <b>Institution: </b>",meta$Institution[1],"\n")
cat("* <b>Source Data: </b>",meta$Source_Data[1],"\n")
cat("* <b>Additional Calculations: </b>",meta$Additional_Calculations[1],"\n")
```

**References** @Santora2020, @Schroeder2022

**Public availability statement** Source data are publicly available.

**Data sources** Surface temperature data are the 2 m temperature levels of the University of California Santa Cruz 31-year historical reanalysis (<https://oceanmodeling.ucsc.edu/reanalccs31/>) and near-real-time (NRT; <https://oceanmodeling.ucsc.edu/ccsnrt/>) data-assimilative models.

**Data extraction**

**Data analysis**
