# Juvenile Salmon
{{< include _setup.qmd >}}

**Description** 
The Northern CCE survey (known as the Juvenile Salmon Ocean Ecology Survey, JSOES) occurs in June and targets juvenile salmon in surface waters off Oregon and Washington. A Nordic 264 rope trawl is towed for 15-30 min at approximately 6.5 km/hr. The gear is fished during daylight hours in near-surface (upper 20 m) waters, which is appropriate for targeting juvenile salmon.

Juvenile salmon data from the Northern CCE are provided by B. Burke, NMFS/NWFSC and C. Morgan, OSU/CIMRS. Data are derived from surface trawls taken during the NWFSC Juvenile Salmon & Ocean Ecosystem Survey (JSOES; https://www.fisheries.noaa.gov/west-coast/science-data/ocean-ecosystem-indicators-pacific-salmon-marine-survival-northern). Similarity analysis and cluster plot by A. Thompson, NMFS/SWFSC.

**Indicators**

```{r}
#| echo: false
#| results: 'asis'
erddap_id='cciea_SM_FBN'
one_id_byquery(erddap_id,"Species")
```

**Data extraction**

```{r}
#| echo: false
#| results: 'asis'
get_erddap_link(erddap_id)
```

**Data analysis**

**References**
