# Juvenile Salmon

**Description** 
The Northern CCE survey (known as the Juvenile Salmon Ocean Ecology Survey, JSOES) occurs in June and targets juvenile salmon in surface waters off Oregon and Washington. A Nordic 264 rope trawl is towed for 15-30 min at approximately 6.5 km/hr. The gear is fished during daylight hours in near-surface (upper 20 m) waters, which is appropriate for targeting juvenile salmon.

Juvenile salmon data from the Northern CCE are provided by B. Burke, NMFS/NWFSC and C. Morgan, OSU/CIMRS. Data are derived from surface trawls taken during the NWFSC Juvenile Salmon & Ocean Ecosystem Survey (JSOES; https://www.fisheries.noaa.gov/west-coast/science-data/ocean-ecosystem-indicators-pacific-salmon-marine-survival-northern). Similarity analysis and cluster plot by A. Thompson, NMFS/SWFSC.

**Indicators**

```{r}
#| echo: false
#| message: false
#| eval: true
source("_getmeta.R")

erddap_id='cciea_SM_FBN'
# just want particular indicators from this dataset
#erddap_query_vals <- c("Yearling Chinook", "Yearling Coho", "Subyearling Chinook")
meta=getMetadata(erddap_id)
num_ind = nrow(meta)
```

```{r}
#| echo: false
#| results: 'asis'
cat("* <b>Species:</b>\n")
for (i in 1:num_ind){
cat("     + ",meta$ERDDAP_query_value[i],"\n")
}
```

```{r}
#| echo: false
#| results: 'asis'
cat("* <b>Component Category: </b>", meta$Component_Section[1],"\n")
cat("* <b>Data Steward: </b>",meta$Contact[1],"\n")
cat("* <b>Institution: </b>",meta$Institution[1],"\n")
cat("* <b>Source Data: </b>",meta$Source_Data[1],"\n")
cat("* <b>Additional Calculations: </b>",meta$Additional_Calculations[1],"\n")
```

**Data extraction**

```{r}
#| echo: false
#| results: 'asis'
cat("ERDDAP&trade; link: <https://oceanview.pfeg.noaa.gov/erddap/tabledap/cciea_EI_FBN.html>",sep="")
```

**Data analysis**

**References**
