
# Marine Heatwaves
{{< include _setup.qmd >}}

**Description** Marine heatwaves (MHW) occur when ocean temperatures are much warmer than usual for an extended period of time; they are specifically defined by the difference between the current temperature and the expected temperature for a specific location and time of year \[1\]. MHWs are a growing field of study worldwide because of their effects on ecosystem structure, biodiversity, and regional economies.


**Indicators**

```{r}
#| echo: false
#| results: 'asis'
erddap_id='cciea_OC_MHW'
one_id_multimeta(erddap_id)
```

**Additional Information**

There is growing recognition that marine heatwaves can have strongly disruptive impacts on the CCE [@morgan2019recent]. Based on an analysis of sea surface temperature anomalies (SSTa) obtained from satellite measurements (OISST); we define marine heatwaves as 1.0 times when normalized SSTa \>1.29 s.d. (90th percentile) of the long-term SSTa time series at a location, and 2. lasts for \>5 days; which are analogous to the thresholds suggested in @hobday2016hierarchical. Here, we further report on statistics concerning large heatwaves (LHW) which were tracked through space and time, with LHW defined as those heatwaves with an area \> 400,000 km2 (these denote the top 20% of all heatwaves by area as measured since 1982 when satellite data became available for tracking.

The underlying climatology used for SST anomaly analysis has changed from 1982-2010, to now encompass 1982-2020; hence small changes in the retrospective analysis of tracked heatwaves reported more recently as compared to previous reports.

**Data extraction**

```{r}
#| echo: false
#| results: 'asis'
get_erddap_link(erddap_id)
```

**References**
