# Maximum Stream Temperatures

**Description** Mean maximum stream temperatures in August were determined from 446 USGS gauges with temperature monitoring capability. While these gauges did not necessarily operate simultaneously throughout the period of record, at least two gauges provided data each year in all ecoregions. Stream temperature records are limited in California, so two ecoregions (Sacramento/San Joaquin and Southern California Bight-Baja) were combined. Maximum temperatures exhibit strong ecoregional differences in absolute temperature (for example, Salish Sea and Washington Coast streams are much cooler on average than California streams).

Freshwater habitat indicators are reported based on a hierarchical spatial framework. The framework facilitates comparisons of data at the right spatial scale for particular users, whether this be the entire California Current, ecoregions within the CCE, or smaller spatial units. The framework we use divides the region encompassed by the CCE into ecoregions (Fig. 1.1), and ecoregions into smaller physiographic units. Freshwater ecoregions are based on the biogeographic delineations in Abell et al. (2008), see also www.feow.org, who define six ecoregions for watersheds entering the California Current, three of which comprise the two largest watersheds directly entering the California Current (the Columbia and the Sacramento-San Joaquin Rivers). Within ecoregions, we summarized data at scales of evolutionary significant units (ESUs) and 8-field hydrologic unit classifications (HUC-8). Status and trends for all freshwater indicators are estimated using space-time models that account for spatial and temporal autocorrelation (Lindgren and Rue 2015).


```{r}
#| echo: false
#| message: false
#| eval: true
erddap_id='cciea_HB_FLOW'
source("_getmeta.R")
meta=getMetadata(erddap_id)
num_ind = nrow(meta)
```


```{r}
#| echo: false
#| results: 'asis'

regions=c("Ecoregion")
nregions=length(regions)
meas=c("August Mean Max stream temperature")
nmeas=length(meas)
for(j in 1:nregions){
  for(k in 1:nmeas){
    cat("**Streamflow ",meas[k]," ",regions[j]," indicators:**\n\n",sep="")
    cat("* <b>",regions[j],"s:</b>\n",sep="")
      for (i in 1:num_ind){
        if(grepl(meas[k],meta$Title[i]) & grepl(regions[j],meta$Title[i])){
  cat("     + ",meta$region[i],"\n")
  cind=i
  }
}

cat("* <b>Component Category: </b>", meta$Component_Section[cind],"\n")
cat("* <b>Data Steward: </b>",meta$Contact[cind],"\n")
cat("* <b>Institution: </b>",meta$Institution[cind],"\n")
cat("* <b>Source Data: </b>",meta$Source_Data[cind],"\n")
cat("* <b>Additional Calculations: </b>",meta$Additional_Calculations[cind],"\n\n")
  }
}
```

**Data extraction**

```{r}
#| echo: false
#| results: 'asis'
cat("ERDDAP&trade; link: <https://oceanview.pfeg.noaa.gov/erddap/tabledap/",erddap_id,".html>",sep="")
```

**Data analysis**
