# Ocean Acidification

```{r}
#| echo: false
#| message: false
#| eval: true
erddap_id='cciea_OC_ARG'
source("_getmeta.R")
meta=getMetadata(erddap_id)
num_ind = nrow(meta)
```

**Description** Ocean acidification (OA) occurs when atmospheric CO2 dissolves into seawater, reduces seawater pH and carbonate ion levels. Upwelling transports low oxygen, acidified waters from deeper offshore onto the continental shelf, where increased community-level metabolic activity can further exacerbate OA [@feely2008evidence]. A key measure of OA is aragonite saturation state, which is related to availability of aragonite (a form of the mineral calcium carbonate) to form or dissolve. Aragonite saturation <1.0 indicates relatively acidified, corrosive conditions that are stressful for many CCE species, particularly shell-forming invertebrates. OA impacts on these species can propagate through marine food webs and potentially affect fisheries [@marshall2017risks]. Aragonite saturation states tend to be lowest during spring and summer upwelling, and highest in winter.

**Newport Line Aragonite Saturation**

```{r}
#| echo: false
#| results: 'asis'

cat("* <b>Locations:</b>\n")
for (i in 1:num_ind){
if(grepl("NH",meta$Title[i])){
  cat("     + ",meta$ERDDAP_query_value[i],"\n")
  cind=i
  }
}
```

```{r}
#| echo: false
#| results: 'asis'
cat("* <b>Component Category: </b>", meta$Component_Section[cind],"\n")
cat("* <b>Data Steward: </b>",meta$Contact[cind],"\n")
cat("* <b>Institution: </b>",meta$Institution[cind],"\n")
cat("* <b>Source Data: </b>",meta$Source_Data[cind],"\n")
cat("* <b>Additional Calculations: </b>",meta$Additional_Calculations[cind],"\n")
```

**Data extraction**

```{r}
#| echo: false
#| results: 'asis'
cat("ERDDAP&trade; link: <https://oceanview.pfeg.noaa.gov/erddap/tabledap/",erddap_id,".html>",sep="")
```


**References**

