# PDO (Pacific Decadal Oscillation)

**Description** The CCLME is driven by atmosphere–ocean energy exchange that occurs on many temporal and spatial scales. The Pacific Decadal Oscillation (PDO) describes North Pacific sea surface temperature (SST) anomalies that may persist for many years. Positive PDOs are associated with warmer SST and lower productivity in the CCE, while negative PDOs indicate cooler SST and are associated with higher productivity.

```{r get-file-from-google-drive}
#| echo: false
#| message: false
#| eval: true
erddap_id='cciea_OC_PDO'
source("_getmeta.R")
meta=getMetadata(erddap_id)
num_ind = nrow(meta)
```

```{r}
#| echo: false
#| results: 'asis'

for (i in 1:num_ind){
cat("<b>",meta$Title[i],"</b>\n\n",sep="")
cat("* <b>Component Category: </b>", meta$Component_Section[i],"\n")
cat("* <b>Data Steward: </b>",meta$Contact[i],"\n")
cat("* <b>Institution: </b>",meta$Institution[i],"\n")
cat("* <b>Source Data: </b>",meta$Source_Data[i],"\n")
if(meta$Additional_Calculations[i]!="")cat("* <b>Additional Calculations: </b>",meta$Additional_Calculations[i],"\n")
}
```

**Data extraction**

```{r}
#| echo: false
#| results: 'asis'
cat("ERDDAP&trade; link: <https://oceanview.pfeg.noaa.gov/erddap/tabledap/",erddap_id,".html>",sep="")
```


