# SST (Sea Surface Temperature)

## Buoy Data {.unnumbered}

**Indicators**

```{r}
#| echo: false
#| message: false
#| eval: true
source("_getmeta.R")

erddap_id='cciea_OC_SST'
meta=getMetadata(erddap_id)
num_ind = nrow(meta)
```


```{r}
#| echo: false
#| results: 'asis'
cat("* <b>Latitudes:</b>\n")
for (i in 1:num_ind){
cat("     + ",meta$latitude[i],"N\n")
}
```

```{r}
#| echo: false
#| results: 'asis'
cat("* <b>Component Category: </b>", meta$Component_Section[1],"\n")
cat("* <b>Data Steward: </b>",meta$Contact[1],"\n")
cat("* <b>Institution: </b>",meta$Institution[1],"\n")
cat("* <b>Source Data: </b>",meta$Source_Data[1],"\n")
cat("* <b>Additional Calculations: </b>",meta$Additional_Calculations[1],"\n")
```

**Data extraction**

```{r}
#| echo: false
#| results: 'asis'
cat("ERDDAP&trade; link: <https://oceanview.pfeg.noaa.gov/erddap/tabledap/",erddap_id,".html>",sep="")
```


## Satellite data {.unnumbered}
Satellite data which has been collected in a similar fashion since 1982, allows for a basin-scale view of sea surface temperature (SST) at up to daily and sub-degree (spatial) resolution.

## Glider data {.unnumbered}
Glider data has also become an increasingly useful tool for analyzing trends in subsurface water temperatures over time. Subsurface gliders, which generally sample in onshore-offshore transects on a weekly to monthly basis, have been in service long enough for the development of climatologies, which are then used to compute temperature anomalies.

**References**

